Two Mode Networks and Relational Similarity

### 2023-08-28 main.tex

Note that for the people, the even-numbered reflection $C^R_p(2)$ assigns centrality based on a formal feature of the \textit{groups} they belong to (in this case, their degree centrality). On the other hand, the odd-numbered reflection $C^R_p(3)$ assigns centrality based on a formal feature of the \textit{members of the groups} they belong to. In the same way, for the groups, the even-numbered reflection $C^R_g(2)$ assigns centrality based on a formal feature of the \textit{people} who belong to them (in this case, their degree centrality). On the other hand, the odd-numbered reflection $C^R_g(3)$ assigns centrality based on a formal feature of the \textit{groups their members belong to}.

@@

\section{Correspondence Analysis and Dual Centralities}

>>>>

Note that for the people, the even-numbered reflection $C^R_p(2)$ assigns centrality based on a formal feature of the \textit{groups} they belong to (in this case, their degree centrality). On the other hand, the odd-numbered reflection $C^R_p(3)$ assigns centrality based on a formal feature of the \textit{members of the groups} they belong to. In the same way, for the groups, the even-numbered reflection $C^R_g(2)$ assigns centrality based on a formal feature of the \textit{people} who belong to them (in this case, their degree centrality). On the other hand, the odd-numbered reflection $C^R_g(3)$ assigns centrality based on a formal feature of the \textit{groups their members belong to}. While these are distinct metrics, in practice the order of nodes in each mode ends up being identical when the ranks ``freeze'' after some number of iterations (proportional to the size of the network).

@@

Figure~\ref{fig:pg-reflections} shows the trajectory of reflective centralities for persons and groups in the Southern Women data \citep{davis1941}.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Plots/pg-reflections.png}
    \caption{Reflective centrality trajectories of persons and groups (even reflections).}
    \label{fig:pg-reflections}
\end{figure}
\section{Correspondence Analysis and Dual Centralities}
